Trans-dimensional Bayesian Inference and Nested Sampling

### 2015-01-31 Documents/Talk/content.tex
starfield image

\begin{frame}[t]{Motivating Problem II}
\begin{itemize}
\item How many galaxies are in this data?
\item Also, what are their positions, sizes, orientations, etc?
\end{itemize}
\begin{center}
\includegraphics[scale=0.35]{../Paper/galaxyfield_data.pdf}
\end{center}
\end{frame}

@@

>>>>

\begin{frame}[t]{Motivating Problem II}
\begin{itemize}
\item How many stars are in these images?
\item Also, what are their positions, fluxes, etc?
\end{itemize}
\begin{center}
\includegraphics[scale=0.35]{test_cases.pdf}
\end{center}
\end{frame}

@@

\begin{frame}[t]{View of data analysis}
All conclusions are probabilities.

The only difference between data analysis methods is what prior information
they assume.
\end{frame}
